%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Jeremy Moyers}{January 21, 1991}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:jeremy.at.jeremymoyers.coml}{jeremy\mbox{}@\mbox{}jeremymoyers.com}\sbull
(858) 775-4489
\\
3130 Groton Way Unit 1\sbull
San Diego\thinspace {\large \sc }\sbull
California

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Education}

\headedsection
  {\href{https://www.calpoly.edu}{California Polytechnic State University, San Luis Obispo}}
  {\textsc{San Luis Obispo, California}} {%
  \headedsubsection
    {Bachelor degree in Computer Science}
    {2014}
    {\bodytext{}}
}
\vspace{-0.8em}


\spacedhrule{0.5em}{-0.4em}

\roottitle{Programming Languages}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {}
  {Swift, JavaScript, C\#, Objective-C, C }

\spacedhrule{1.6em}{-0.4em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://seamgen.com}{Seamgen, LLC}}
  {\textsc{Nov \apo15 -- Present}} {%
  \vspace{0.8em}
  
  \headedsubsection
  {AvaGen, Avellino Labs USA Inc, Full Stack Developer}
  {6 months}
  {\bodytext{\emph{Native Swift, React/Redux web frontend, C\# .net core} \vspace{0.4em} \\ Optimized for iPad and iPhone AvaGen enables physicians to collect patient consent for DNA testing and notifies patients when test results are available from the lab. Technologies include UIKit and Core Location.}}

  \headedsubsection
  {Disability Insurance Services, Front End Developer}
  {4 months}
  {\bodytext{\emph{React Redux} \vspace{0.4em} \\ A web portal used by insurance brokers for cataloging client information and generating different insurance rate proposals.}}

  \headedsubsection
  {Specialty Produce, Extraordinaire Tomatoes Inc, Mobile Developer}
  {1.5 years to present}
  {\bodytext{\emph{Xamarin Forms} \vspace{0.4em} \\ A mobile encyclopedia with thousands of produce items and recipes. Daily updates available to subscribers through Apple In-app purchases and Google Play In-app Billing.}}

  \headedsubsection
  {Bump App, Bump LLC, Mobile Developer}
  {3 months}
  {\bodytext{\emph{Xamarin Native} \vspace{0.4em} \\ A social network for sharing experiences and exploring your surroundings in real time. Technologies used include Core Location, MapKit and AVFoundation.}}

   \headedsubsection
  {Script Save Well RX, Medical Security Card Company LLC, Mobile Developer}
  {6 months}
  {\bodytext{\emph{Xamarin Native} \vspace{0.4em} \\ Script Save Well Rx enables users to search for savings on prescription medicines and compare prices at pharmacies in their area. Technologies used include Core Location, MapKit and iBeacon.}}

   \headedsubsection
  {Referral Maker CRM, Buffini and Company, Mobile Developer}
  {4 months}
  {\bodytext{\emph{Xamarin Native} \vspace{0.4em} \\ Real Estate coaching CRM application to help agents generate consistent and predictable stream of referred and repeat business. Technologies used include Contacts, Core Location, AVFoundation and MapKit.}}

   \headedsubsection
  {Rocketing for Instagram, Rocketing Apps LLC, Mobile Developer}
  {6 months}
  {\bodytext{\emph{Native Swift} \vspace{0.4em} \\ Social application for finding people places parties anywhere in the world. Technologies used include Contacts, Core Location, AVFoundation and Core Animation}}  
  
   \headedsubsection
  {Onsite Ticketing Application, San Diego Comic Con, C\# WPF Developer}
  {6 months}
  {\bodytext{\emph{C\# WPF} \vspace{0.4em} \\ OSPA (onsite printing application) a windows desktop application for managing the comic con convention. OSPA's features include bulk printing tickets, checking guests into the event, purchasing new tickets, distributing tickets for companies and more.}}
  
  
}
\vspace{0.8em}
\headedsection  % sets the header for a subsection and contains usually body text
  {\href{http://www.hotbsoftware.com}{HOTB Software Solutions} }
  {\textsc{Aug \apo14 -- Nov \apo15}} {%
  \headedsubsection
    {iOS Developer}
    {}
    {\bodytext{\emph{Native Objective-C} \vspace{0.4em} \\Developed a native iOS app for a social network. Contributed to the backend API design of utilizing AWS dynamoDB and Amazon s3. Administered the app through the App Store approval process.}}
}

\vspace{0.8em}
\headedsection
  {\href{www.google.com}{HomeSlice}}
  {\textsc{Mar \apo13 -- Apr \apo14}} {%

  \headedsubsection
    {Full Stack Developer}
    {}
    {\bodytext{\emph{Native Objective-C, Ruby on Rails} \vspace{0.4em} \\ HomeSlice is a social network enabling roommates to their manage chores, supplies, and bills. Designed and developed the native HomeSlice iOS app and the Ruby on Rails API.}}
}

\vspace{0.8em}
\headedsection
  {\href{www.google.com}{Rosetta/Level Studios}}
  {\textsc{Oct \apo11 -- Mar \apo13}} {%

  \headedsubsection
    {iOS Engineering Intern}
    {}
    {\bodytext{\emph{Native Objective-C} \vspace{0.4em} \\ Built an internal facing iOS application with a cakePHP RESTful API used for managing project statuses of different development teams.}}
}

\vspace{0.8em}
\headedsection
  {\href{www.google.com}{Northrop Grumman}}
  {\textsc{July \apo10 -- Dec \apo10}} {%

  \headedsubsection
    {Summer Intern}
    {}
    {\bodytext{\emph{VB.NET} \vspace{0.4em} \\ Built and designed an internal facing .net Web Application for reporting maintenance issues to the companies facilities department.}}
}

\spacedhrule{0.5em}{-0.4em}





\end{document}

＀
